---
title: "Week 3 Assignment - Developing Data Products"
author: "jc"
date: "8/6/2020"
output: ioslides_presentation
---


## Instructions

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

### Outline

Brief presentation with the following features:

- Use of the plotly library.
- Interactive plots over the mtcars dataset using plotly.

## Interactive mtcars!
```{r mt1, eval=FALSE}
library(plotly)
f <- list(
  family = "Courier New, monospace",
  size = 14,
  color = "#2f7f7f"
)
x <- list(
  title = "QT",
  titlefont = f
)
y <- list(
  title = "MPG",
  titlefont = f
)
fig <- plot_ly(mtcars, x = mtcars$qsec, y=mtcars$mpg, mode="markers", 
        type="scatter",color=as.factor(mtcars$cyl), size=mtcars$hp)
fig <- fig %>% layout(xaxis = x, yaxis = y)
fig

```
## QT vs MPG
```{r mt2, echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
f <- list(
  family = "Courier New, monospace",
  size = 14,
  color = "#2f7f7f"
)
x <- list(
  title = "QT",
  titlefont = f
)
y <- list(
  title = "MPG",
  titlefont = f
)
fig <- plot_ly(mtcars, x = mtcars$qsec, y=mtcars$mpg, mode="markers", 
        type="scatter",color=as.factor(mtcars$cyl), size=mtcars$hp)
fig <- fig %>% layout(xaxis = x, yaxis = y)
fig

```